Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-08-31 1_introduction/introduction.tex
no message

The approach proposed in this thesis is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis. Finally recommendation generation stage is undertaken to create learning opportunities for each organization. With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps. Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs. Performance of methodology is assessed with a defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

>>>>

The approach proposed in this study is a four-stage solution and it starts with mining the process models of organizations; followed by performance indicator analysis and then mismatch pattern analysis. Finally recommendation generation stage is undertaken to create learning opportunities for each organization. With this approach it is aimed to help business process management users to focus on the potentially important parts of their business maps. Proposed methodology is implemented in ProM framework \cite{verbeek2010prom} as a set of plugins corresponding for each stage and packaged under the name of \textit{CrossOrgProcMin} and tested on a synthetic and real-life event logs. Performance of methodology is assessed with a defined evaluation metrics for each stage and resulting recommendations are presented to show how this approach helps users to focus on learning opportunities between organizations with a performance improvement potential.

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

>>>>

 Within the process mining framework, there are various different process mining algorithms proposed which have the same aim of discovering underlying processes. Considering the underlying approaches undertaken, algorithms can be grouped as $\alpha$-algorithms \cite{van2004workflow, de2004process}, inductive approaches \cite{herbst1998integrating, herbst2000dealing}, hierarchical clustering \cite{greco2005mining}, genetic approaches \cite{van2005genetic, esgin2010hybrid}, and heuristic approaches \cite{esgin2009hybrid}. Considering the scope of this study; process discovery operations are undertaken with inductive methods which is a robust, repeatable and mature set of approaches.
